*This text will appear italicized!*

**This text will appear bold!**

# This is a primary heading
## This is a secondary heading
### This is a tertiary heading

- first item in list
- second item in list
- third item in list

1. first item in list
2. second item in list
3. third item in list

Links
[Johns Hopkins Bloomberg School of Public Health](http://www.jhsph.edu/)
[Download R](http://www.r-project.org/)
[RStudio](http://www.rstudio.com/)

Advanced Linking

I spend so much time reading [R bloggers][1] and [Simply Statistics][2]!
 [1]: http://www.r-bloggers.com/ "R bloggers"
 [2]: http://simplystatistics.org/ "Simply Statistics" 
 
 
 ============================
 
 My First R Markdown File
 ====================
 
 This is my first R markdown file.
 
 Here, we're going load some data.
 
```{r}
library(datasets)
data(airquality)
summary(airquality)
```
 
Let's first make a pairs plots of the data

```{r}
pairs(airquality)
```

Here's a regretion model of ozone and wind, solar radiation, and temperature.
```{r}
library(stats)
fit <- lm(Ozone ~Wind + Solar.R + Temp, data = airquality)
summary(fit)
```
## Introduction

 
 Let's first simulate some data.
```{r simulatedata, echo=TRUE}
 x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```

 here is a scatterplor of the data.
```{r scatterplot, fig.height=4}
 par(mar = c(5,4,1,1), las =1)
 plot(x,y,main = "My Simulated Data")
```

 here is a table of regression coefficients.
```{r showtable,results="asis"}
 library(xtable)
 xt = xtable(summary(fit))
 print(xt, type = "html")
```

