---
title: "Statistical Inference Course Project, Part2 - ToothGrowth analysis"
author: "Rodrigo"
date: "September 24, 2015"
output: pdf_document
---

In this second part of the project, we analyze the ToothGrowth data in the R datasets package.
The dataset contains 60 observations, length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1 and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

First we load the data and perform some basic exploratory data analyis

```{r}
library(ggplot2)
library(datasets)
data(ToothGrowth)
str(ToothGrowth) # internal strcuct of dataset
head(ToothGrowth)
summary(ToothGrowth)
```

```{r}
plot <- ggplot(ToothGrowth, 
               aes(x=as.factor(dose),y=len,fill=as.factor(supp)))
plot + geom_boxplot(notch=F) + facet_grid(.~supp) +
     scale_x_discrete("Dosage (Milligram)") +   
     scale_y_continuous("Length of Teeth") +  
     ggtitle("Relation tooth lenght and dose levels for orange juice (OJ) and ascordic acide(VC)")

```

The chart aboove shows that there is a rcorrelation between the tooth length and the dose levels of Vitamin C, for both delivery methods: orange juice (OJ) and ascordic acide(VC).

Tabulating the delivery method by the dose levels of vitamin C

```{r}
table(ToothGrowth$supp, ToothGrowth$dose)

```



We can also use regression analysis to identify the effect of the dose.
The regression anslysis can help us to answer the following question:
"How much of the variance in tooth length, if any, can be explained by the supplement type?"


```{r}
fit <- lm(len ~ dose + supp, data=ToothGrowth)
summary(fit)

```

One can see that there is 70% of the variance in the data and 
The intercept `r fit$coefficients[[1]]`, means that with no supplement of
Vitamin C, the average tooth length is `r fit$coefficients[[1]]` units. 
The coefficient of `dose` is `r fit$coefficients[[2]]`. 
One can interpreted this as an increasing the delivering dose 1 mg could increase the tooth length `r fit$coefficients[[2]]` units.

The last coefficient is for the supplement type. 
Since the supplement type is a categorical variable, dummy variables are used. 
Moreover, delivering a given dose as ascorbic acid, without changing the dose, would result in
`r abs(fit$coefficients[[3]])` units of decrease in the tooth length. 

Using Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose:

```{r}
confint(fit)
```

We can conclude that collecting a different set of data and
estimate parameters of the linear model over end over again,
the coefficient estimations will be in the ranges above in 95% of the time.

Thi null hypothesis in this case is that the coefficients are
zero, and the no tooth length variation is explained by that variable.
As one can see the p-values are less than 0.5. 
As a result the null hypothesis is rejecting. 
In addition, each variable explains a significant portion of variability in tooth length,
assuming the significance level is 5%.

